On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 bqp.tex
Specify dependence on security param
Make editorial changes

\section{Constant-Round Blind Delegation for BQP}
\label{sec:BlindBQP}

@@

\begin{thm}
	\Ethan{Main theorem of the section}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate, which we'll call $\ket{\psi_x}$. See the excellent text \cite{kitaev2002classical} for details.
According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
We'll also summarize said proofs in \cref{sec:Hamiltonian} for our $\SampBQP$ construction.

@@

\begin{protocol}{Protocol for $\BQP$}
	\label{proto:BQP}
	Let $n$ be the number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier sends $x$ to the prover
		\item The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
	The subsequent underlying QMA check also has overwhelming probability of acceptance.
\end{proof}

\begin{thm}
	\protoref{BlindBQP} has negligible soundness
\end{thm}
\begin{proof}
	The verifier's actions is equivalent to first decoding the prover's message then measuring it.

@@

\floatname{algorithm}{Algorithm}

>>>>

\section{Delegation for BQP}
\label{sec:BlindBQP}

@@

\begin{thm}
	\Ethan{Main theorem of the section}
	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate $\ket{\psi_x}$ with some inverse polynomial gap between the completeness and soundness parameters.
See the excellent text \cite{kitaev2002classical} for details.
According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
We'll also summarize said proofs in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

@@

\begin{protocol}{Protocol for $\BQP$}
	\label{proto:BQP}
	Let $n$ be the number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier sends $x$ to the prover
		\item The honest prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
	The subsequent underlying QMA check also has overwhelming probability of acceptance.
\end{proof}

\begin{thm}
	\protoref{BlindBQP} has negligible soundness in both $T$ and $\lambda$
\end{thm}
\begin{proof}
	The verifier's actions is equivalent to first decoding the prover's message then measuring it.

@@

\begin{rmk}
	The same construction works for $\FBQP$ too. \Ethan{maybe say more?}
\end{rmk}

### 2020-02-05 preliminaries.tex
Make editorial changes

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms \hannote{ protocols?} $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
		\item $\bbV$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part. The classical part is a $\BPP$ machine. The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits. At any given time, the verifier is not allowed to possess more than $\tau$ qubits. The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
		 \item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially\hannote{poly in what} many bits to either direction. 
		 \item The protocol\hannote{?} is run by steps. At any given step, either the verifier or the prover performs computations on their registers and send bits and qubits through the relevant channels to the other party.	\hannote{redundant?} 
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) For all $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.

$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$

@@

\begin{dfn}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
\end{dfn}

The constructions in \cite{mahadev_qfhe}, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$, has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
\end{itemize}

Furthermore, one could either decode or measure first, in the following sense:
\begin{lemma}
	\label{decodeMeasureOrder}
	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{lemma}
To the knowledgable reader, this is done simply by storing the so-called quantum-capable ciphertext also as qubits.

>>>>

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a protocol $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
		\item $\bbV$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part. The classical part is a $\BPP$ machine. The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits. At any given time, the verifier is not allowed to possess more than $\tau$ qubits. The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
		\item There is also a classical communication channel between the prover and the verifier, which can transmit $\poly(\abs{x})$ many bits to either direction. 
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) For all $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $L$.

\Ethan{To be pedantic, the above doesn't imply Dec undoes Enc even if we sub in $f=\id$.}

@@

\begin{dfn}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
\end{dfn}

Now we present the quantum homomorphic encryption scheme in \cite{mahadev_qfhe}.
It admits a classical client; one could do the encryption classically, and the decryption is compatible with $X$ and $Z$ measurements.
In general, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then it can be used as a compiler to achieve blindness.

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{I think this point is obvious?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}
